---
title: "Answer to Class Question"
author: "John Little"
date: "`r Sys.Date()`"
output: 
  html_notebook: 
    number_sections: yes
    toc: yes
    toc_float: yes
---

# Question

Several workshop attendees asked how to isolate the data from the data structure.  In other words, How can I get the data value from a single variable cell.  A closely related question is how to report, dynamically, a data value derived programatically? 

> Which restaurant has the most expensive item(s)?  What are those item(s)?

This relates to the *Intro to R* workshop for which documentation can be found in the [intro2r.rev GitHub repository](https://github.com/data-and-visualization/intro2r.rev).

## TL;DR Answer

> answer$itemName

# Packages

Load the tidyverse package.  

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

In the code chunk, above, I also used the following arguments to suppress warnings, because I do not want code warnings in my report.

`{r message=FALSE, warning=FALSE}`

# Load Data

I'll load the brodheadCenter.csv file and assign that object in memory.  This is done using the `readr::read_csf()` function.  `reader` is automatically attached by attaching the `tidyverse` package, above.

```{r message=FALSE, warning=FALSE}
brodhead <- read_csv("data/brodheadCenter.csv")
```

# Derive Answer

In the code chunk, below, let's transform the data in two different ways.  Assign the answers to unique objects names:  `answer` and `answer2`.  There are a few differences in the two Tibble answers.  

```{r echo=TRUE}
answer <- brodhead %>% 
  arrange(desc(cost)) %>% 
  filter(type == "restaurant") %>% 
  select(name, type, itemName, cost) %>% 
  head(1) 

answer2 <- brodhead %>% 
  select(name, type, itemName, cost) %>% 
  filter(type == "restaurant",
         cost == max(cost)) 
```

The first Tibble, `answer`, consists of 1 row and 4 columns.  That's sufficient to answer the first part of the question:  "Which restaurant has the most expensive item(s)?"

The other Tibble, `answer2`, consists of 3 rows and 4 columns.  This is necessary to answer the question, "What are those item(s)?".  Just to be clear, we don't need both tibbles, because all of the information in `answer` is also in `answer2`.  This redundancy is only useful to illustrate that R supports different approaches to data wrangling.

In the next section we will report those answers dynamically.

##  Look at the derived data 

```{r}
answer
answer2
```

- `answer` has a data structure class of: `r class(answer)`.  
- `answer2` has a data structure class of: `r class(answer2)` consisting of `r nrow(answer2)` rows and `r ncol(answer2)` variables.  Each column is a vector.  I want only the first row to answer some parts of the question -- since the values in the vector are identical. The `itemName` vector, however, has different values and I want all three values.

# Compose the Answer 

To answer the question, "Which restaurant", simply call the `name` variable in the single row Tibble, `answer`.  For example...


```{r}
answer$name
```

## Subsetting 

It's possible to isolate the rows and columns of a Tibble (data frame) using bracket notation `[` `]`.  You can use numeric values to identify rows, and then columns.  

>  answer2[1,4]

This code will take the first row, of the fourth column.  

Alternatively, isolate a column variable within a Tibble using a `$`, to separate the Tibble name from the variable name.  

> answer2$cost

Both methods return a vector.  And now you may need to subset the vector.

`answer2$itemName` is a vector of 3 elements.  It's simple to reference a single element using bracket notation surrounding the position of the element.  Or you can reference a range of vector elements, e.g. `answer2$itemsName[2:3]`

> answer2$itemName[2]

To present all elements in the vector, simply reference the variable name as follows

> answer2$itemName

```{r}
answer2$itemName
```

The vector elements are displayed differently, depending on whether you are viewing the code chunk (or console) output, or viewing the report output.  Outside of the R Notebook -- e.g. in an MS Word or  HTML derived report -- the default behavior presents the vector as comma separated values.  Inside an R Notebook the value of the vector can be seen above.


###### http://r4ds.had.co.nz/vectors.html#vector-subsetting

## Integrated Prose and Code

The **`r answer$name`** *`r answer$type`* has the most expensive item(s) at $`r answer$cost`.  Those item(s) are 
`r answer$itemName`.

The **`r answer2$name[1]`** *`r answer2$type[1]`* has the most expensive item(s) at $`r answer2$cost[1]`.  Those item(s) are 
`r answer2$itemName`.

> To see how this is done, review the integrated R Markdown and R code in the R Notebook: [`answers_from-class-question.Rmd`](https://raw.githubusercontent.com/data-and-visualization/intro2r.rev/master/answer_from-class-question.Rmd)

The answers above are derived dynamically (or programatically) and integrated into the report (i.e. this is "literate code").  This means the outcome of the report changes as the data changes.  Meanwhile, the prose remains the same.  To see how this is done, look at the [`answers_from-class-question.Rmd`](https://raw.githubusercontent.com/data-and-visualization/intro2r.rev/master/answer_from-class-question.Rmd) file.

## Further Variations

There are additional function which can manage the insertion of additional text and symbols between the vector values, i.e. commas, conjunctions, symbols, etc. (e.g. $, the oxford comma, etc.).  Those functions include `glue::glue`, `paste`, `paste0`, and `print`.  For the moment let's call this question answered. Because, part of the **fun** in [R] is learning more about [R].  

https://rfun.library.duke.edu




