---
title: "Closing Thoughts"
date: "`r Sys.Date()`"
author: "by Anton Chigurh \u203d"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
  word_document:
    toc: yes  
---

# Load Packages

```{r include=FALSE}
library(tidyverse)
library(knitr)
```

This document uses two packages

- `library(tidyverse)`
- `library(knitr)`

# Alter `output:` in YAML header 

```
---
title: "Closing Thoughts"
date: "`r Sys.Date()`"
author: "\u203d"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
  word_document:
    toc: yes  
---
```

# Example Table 

`kable` works in both HTML & MS Word.  Note that an interactive HTML table does not print very nicely to a Word file.  An alternative is `xtable`.


```{r}
starwars %>% 
  arrange(desc(height), desc(name)) %>% 
  select(1:6) %>% 
  head(15) %>% 
  knitr::kable()
```

> Reading this report as a MS Word document, it should be obvious why an interactive HTML table does not work very well

# Alter settings inside code chunks

- Affect code chunk outputs:  suppress warnings, or show output only, etc.

lines:

- 37 : no warnings
- 62 : no warnings ; "show nothing (run code)"
- 66 : show output only